\documentclass{sobCV}[2015/09/08]




\begin{document}

   \name{Staffan}{Björnson}

   \longcontact{Staffan Bjornson}
               {Fågelängsvägen 36}
               {179 75 Ska}
               {2015-09-09}
               {+46 705 86 94 08}
               {staffan@toor.se}


   % A quote that defines you
   \userquote{If you ever start taking things too seriously, just remember that we are talking monkeys on an organic spaceship flying through the universe.}{The quote Guy}


   % Your job experience 
   \section{Experience}
   \experiencenode{Job title 2}{Company}{2014 -- Now}{sep to now}{
      Planing and designing of test environment with new features and function. Automatic OS deployment, directory server, certificate system and HSM integration. System wide functional testing and regression testing of terminal management systems.

      \loopEx{%
         Automatic Operating System deployment,
         Directory server and MIT Kerberos etc.,
         Regression testing ,
         Administration tool development (Bash, Python \& Java),
         System documentation (End user guides and technical documentation for developers),
         In charge of product build and release with in the development team
      }
   }

   \experiencenode{Job title 2}{Company}{2013 -- 2014}{aug to sep}{
      A lot of interesting things about your old job
   }



   % Your education 
   \section{Education}
   \ednode{University of Nowhere}{2004 -- 2008}{%
      I attended the University of Nowhere from 2004 to 2008.
   }

   \ednode{University of Nowhere}{2001 -- 2004}{%
      I attended the University of Nowhere from 2004 to 2008.
   }

   \ednode{University of Nowhere}{1998 -- 2001}{%
      I attended the University of Nowhere from 2004 to 2008.
   }

   % Other courses 
   \section{Other training programs \& courses}
   \coursenode{University of Nowhere}{Company}{%
      I attended the University of Nowhere from 2004 to 2008.
      }

   \coursenode{Course name}{Company}{%
      I attended the University of Nowhere from 2004 to 2008.
      }

   \section{Language}


   \section{Driving license}

   \section{Skills}

\end{document}