\documentclass{sobCV}[2017/07/08]

\begin{document}
   \name{Staffan}{Björnson}
   \longcontact{Staffan Björnson}
               {Blåskbacksvägen 93}
               {179 62 Stenhammra}
               {0705-86 94 08}
               {2019-10-02}
               {staffan@toor.se}

% =============================================================================
% A quote that defines you
   \userquote{Better to do something properly from the beginning,\\than having to go back to do it again}

% =============================================================================
% Your job experience 
% =============================================================================
   \section{Experience}
      \experiencenode
      % =======================================================================
      {Test Consultant}                % Set your jobe title
      {Assigned at Kambi Group plcs (Esplanad Business Solutions AB)}% Company name
      {2015 -2019}                        % What year did you start and end
      {Current}{                           % Specifye month
      % =======================================================================
      % What whas the main tasks thith the job. 
      % Use comma (,) to separate jthe tasks.
      % =======================================================================
          Sole tester in an agile team,
          Front and backend testingk,
          Focus on exploritory testing,
          Automated UA testing (Python based helper framework)
      }{
      % =======================================================================
      % Description of your job 
      % =======================================================================
          As a tester in an agile team, I have developed test strategies and 
          performed manual tests with a strong focus on exploretory tests. In a
          team project I have been responsible for developing automatic 
          blackbox tests, with a Python based test framework, which is 
          integrated with the build and deploy process of the team application.
      }
      \experiencenode
      % =======================================================================
      {Test Manager/Tester/Junior Developer}         % Set your jobe title
      {Esplanad Business Solutions AB}        % Company name
      {2015 - 2018}                        % What year did you start and end
      {nov to nov}{                           % Specifye month
      % =======================================================================
      % What whas the main tasks thith the job. 
      % Use comma (,) to separate jthe tasks.
      % =======================================================================
      Server Maintenance (Windows and Linux),
      Backend/Frontend testing (TMS/PPL),
      PoS Terminal brandtesting and certification,
      Administration tool development (Bash Python and Java),
      System documentation
      }{
      % =======================================================================
      % Description of your job 
      % =======================================================================
      Testing of Terminal Management System (TMS), Windows with a .Net 
      frontend and a Java backend with PostgreSQL database running on Linux.  
      Testing and certification of PoS Terminals. In charge of server 
      maintenance and up keep of the VMware envoronment. Jirs/Confluence 
      administrator for user and developers documentation.
      }
      \experiencenode
      % =======================================================================
      {Test Environment Engineer}             % Set your jobe title
      {Verifone}                              % Company name
      {2014 -- 2015}                          % What year did you start and end
      {sep to nov}{                           % Specifye month
      % =======================================================================
      % What whas the main tasks thith the job. 
      % Use comma (,) to separate jthe tasks.
      % =======================================================================
      Automatic Operating System deployment,
      Directory server and MIT Kerberos etc.,
      Regression testing ,
      Administration tool development (Bash, Python and Java),
      System documentation (User and developers documentation),
      In charge of product build and release with in the development team
      }{
      % =======================================================================
      % Description of your job 
      % =======================================================================
      Planing and designing of test environment with new features and 
      functions. Automatic OS deployment, directory server, certificate system 
      and HSM integration. System wide functional testing and regression 
      testing of terminal management systems.

      In charge of product builds and releases with in the development team.
      }

      \experiencenode
      % =======================================================================
      {Software Test Engineer}               % Set your jobe title
      {Verifone}                             % Company name
      {2014 -- 2014}                         % What year did you start and end
      {jan to sep}{                          % Specifye month
      % =======================================================================
      % What whas the main tasks thith the job. 
      % Use comma (,) to separate jthe tasks.
      % =======================================================================
         White/Black-box testing,
         Regression testing,
         Test environment administration and configuration
      }{
      % =======================================================================
      % Description of your job 
      % =======================================================================
      Testing and verification of host applications, payment gateway system, 
      terminal management systems and EMV PoS terminals. This involves System 
      wide, component, regression testing and maintenance of in house build 
      terminal management system.

      Testing is done in conjunction with the developers in tight scrum teams 
      where testers and developers work closely together. 

      Administrate, configure and build test environment (CentOS/RHEL) for POS 
      terminals and payment gateways. Including new features and development.
      }

% =============================================================================
% Your Education
% =============================================================================
   \section{Education}
   \ednode
      {CAS (Värmdö KomVux) \& Åsö Gymnasium}
      {1998 -- 2000}{%
      Operatingsystem, Graphic comunication (A \& B), Webbdesign, Filosefy, C++ Programmering etc.
   }

   \ednode
      {VTG, Värmdö Tekniska Gymnasium}
      {1995 -- 1998}{%
         Three years, automotive technical training.
      }



% =============================================================================
% Other training programs & courses
% =============================================================================
   \section{Other training programs \& courses}
%      \coursenode
%      {Verifone}
%      {2015}
%      {ISTQB Certified Tester}{%
%         ISTQB Foundation is a course that gives you an understanding of the basics of testing and quality assurance of software.
%      }
      \coursenode
      {Udemy}
      {2019}
      {Robot Framework Test Automation Level 1 and Level 2}{%
         Course in which rights apply to the company and which rights the customer have.
      }

   \coursenode
      {Udemy}
      {2019}
      {REST APIs with Flask and Python}{%
         Training programs in communication and change management.
      }

% =============================================================================
% Skills
% =============================================================================
   \section{Skills}
      \skills{Operating Systems}{
         GNU/Linux RedHat/CentOS) ,
         Windows Server ,
         *NIX (BSD \& Solaris)
         }
      \skills{Programming}{
         Bash,
         Java,
         Python,
         C/C++,
         LaTeX,
         Javascript               
         }

      \skills{Programs}{
         PostgreSQL,
         Jenkins,
         Maven,
         VMware,
         Jira,
         Confluense,
         Satellite/Spacewalk,
         Eclipce,
         IntelliJ,
         Git,
         SVN
      }

   \section{Language}
      \spokenLanguage{
         Swedish,
         English
      }

   \section{Driving license}
      \license{
         A -- Motorbike,
         B -- Car 
      }





\end{document}
